### 2021-07-06 docs/manuscript/manuscript.tex
Rephrase study description

In this study, we used a genetic algorithm to generate a set of 2061 three-node GRNs
including single and multiple input topologies that were able to interpret a morphogen
signal and respond to it generating a striped pattern of gene expression in order to
analyse the role of network motifs in this process and its dynamic properties.

>>>>

In this study, we apply a Markov chain Monte Carlo (MCMC)-like algorithm to
probe the design space of three-node GRNs looking for topologies capable of
translating a morphogen gradient  (input signal) into a striped pattern of gene
expression (phenotype). Importantly, unlike most previous computational
studies, here we allowed any node (e.g. gene) in a GRN to perceive the input
signal in varying ways, and selected the best performing GRNs based on a
fitness criterion used to assess the quality of the phenotype with respect to
a prescribed optimal pattern. Based on this computational strategy, we were
able to uncover a great variety of distinct classes of network topologies that
tend to form a complex interconnected meta-graph that could be easily
traversed throughout evolution via single changes in the wiring of the
different GRNs.
